taxadb: A High-Performance Local Taxonomic Database Interface

### 2018-12-30 paper/manuscript.Rmd
support ott

```{r}
bbs_ids <- 
data_frame(species = species_list) %>% 
  mutate(gbif = get_ids(species, "gbif", "prefix"),
         col = get_ids(species, "col", "prefix"),
         itis = get_ids(species, "itis", "prefix"),
         ncbi = get_ids(species, "ncbi", "prefix"),
         wikidata = get_ids(species, "wd", "prefix")) 
```

>>>>

```{r}
bbs_ids <- 
data_frame(species = species_list) %>% 
  mutate(gbif = get_ids(species, "gbif", "prefix"),
         col = get_ids(species, "col", "prefix"),
         itis = get_ids(species, "itis", "prefix"),
         ncbi = get_ids(species, "ncbi", "prefix"),
         wikidata = get_ids(species, "wd", "prefix"))

```{r}
ott_ids <- ids(species_list, "ott")
```
